Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-20 ms.tex
added typical error bars to time series.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
Quiescent intervals with low transit activity are identified from the amplitude.
The first principal component tracks closely with the amplitude.
The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.}\label{fig:tserPC}
\end{centering}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.99\textwidth]{pc_tser_w_quiescent.pdf}
\caption{Time series of the transit amplitude and principals components of the Kepler data (Left panel).
We also show the ground-based photometry from \citet{schlawin2016kic1255} and this work (Right upper plot).
Quiescent intervals with low transit activity are identified from the amplitude \added{and highlighted in orange. 
Typical (median) error bars for the time series are shown as red error bars at arbitrary positions.}
The first principal component tracks closely with the amplitude.
The second principal component shows periodicity at 491 days, indicating possible long-term evolution of dust grain particle sizes.
}\label{fig:tserPC}
\end{centering}
\end{figure*}
